% master.tex : master file for the project
% ------------------------------------------------------------------------------
% This is the main file in the project, which collects the contents from all the
% input files (text, images, literature databases, etc.).

% The 'book' class is a document class with many flexible options.
% See https://tex.stackexchange.com/a/36989/118167
\documentclass[11pt,a4paper,twoside,openright,english]{book}
 
% Some top level variables that are used to automatically input title, authors,
% etc. in the title page and front page.
\def \projecttitle       {Advanced Topics with Applications}
\def \projectsubtitle    {Rough Volatility}
\def \projecttheme       {Project Theme}
\def \projectdegree      {Mathematics-Economics}  % or Mathematics-Economics/Technology
\def \projectperiod      {Autumn Semester 2023}
\def \projectnumber      {P9}
\def \projectgroup       {1.204f}
\def \projectauthors     {
  Christian Bang Jensen \\
  % ...
}
\def \projectsupervisors {
  Orimar Sauri\\
  Toke Zinn\\
  % ...
}

% The preamble, i.e. all the settings and commands that go before actual
% document contents, in this template is handled in the single file aaumath.sty,
% which defines a package that can be loaded here with \usepackage.
\usepackage{aaumath}
\usepackage{soul}
\usepackage{booktabs}
\usepackage{float}


\usepackage{algorithm}
\usepackage{algpseudocode}

% All contents of the document go between the \begin and \end commands for the
% 'document' environment.
\begin{document}

% The front matter is not counted in the numbered pages and are instead numbered
% with roman numerals. This consists of, for example, the front page, title
% page, preface, and table of contents.
\frontmatter
\include{incl/misc/frontpage}
\include{incl/misc/titlepage}
\include{incl/misc/preface}
\include{incl/misc/listofnotation}
\include{incl/misc/contents}
% The main matter is were the bulk of your work goes. Pages and headings have
% arabic numbers.
\mainmatter

%\include{chapters/GeneralTheory/Maingeneraltheory}
%INTRODUKTION
\include{chapters/Introduction/Introduction}

%THEORY CHAPTERS
\include{chapters/Theory/SDEs}
\include{chapters/Theory/FractionalBM}
%\include{chapters/Theory/ExtraTheory}

%APPLICATION CHAPTERS
\include{chapters/Application/VolatilityModelling}
\include{chapters/Application/OptionPricing}
% Input files should be partitioned such that each file corresponds to one
% chapter. The \include command forces a page break and inserts the contents of
% the input file.

% \include{incl/main/example1}
% \include{incl/main/example2}
% ...

% Appendices are included inside an appendices block, which enumerates chapters
% with letters, starting from A, instead of numbers.
%\begin{appendices}
%\include{incl/app/allcode}
%\end{appendices}

% The backmatter is for extra stuff. Headings are not numbered.
\backmatter

% Automatic list of references, based on which references in the literature
% database files were referenced throughout the document.

%\bibliographystyle{apalike}
%\bibliography{
%  incl/bib/books,
%  incl/bib/articles,
%  incl/bib/software
%}
\begin{thebibliography}{}
\bibitem{bollerslev}
Andersen, T.G., Bollerslev, T., Diebold, F.X., and Ebens, H. \textit{The Distribution of Realized Stock Return Volatility}. Journal of Financial Economics, 61(1):43-76 (2001).

\bibitem{barndorff}
Barndorff-Nielsen, O.E., Corcuera, J.M., and Podolskij, M. \textit{Limit Theorems for Functionals of Higher Order Differences of Brownian Semi-Stationary Processes}. CREATES Research Paper (2009).

\bibitem{simfBMappendix}
Banna, O., Mishura, Y., Ralchenko, K., and Shklyar, S. \textit{Fractional Brownian Motion: Approximations and Projections}, 1st edition. Wiley (2019).

\bibitem{pricing}
Bayer, C., Friz, P., and Gatheral, J. \textit{Pricing under Rough Volatility}. Quantitative Finance, 16(6):887-904 (2016).

\bibitem{hybrid}
Bennedsen, M., Lunde, A., and Pakkanen, M.S. \textit{Hybrid scheme for Brownian semistationary processes}. Finance and Stochastics, 21(4):931-965 (2017).

\bibitem{bergomi}
Bergomi, L. \textit{Smile Dynamics II}. Risk October, p. 67-73 (2005).

\bibitem{intbook}
Biagini, F., Hu, Y., Øksendal, B., and Zhang, T. \textit{Stochastic Calculus for Fractional Brownian Motion and Applications}, 1st edition. Springer (2008).

\bibitem{bjork}
Björk, T. \textit{Arbitrage Theory in Continuous Time}, 4th edition. Oxford University Press (2019).

\bibitem{black1973}
Black, F., and Scholes, M. \textit{The Pricing of Options and Corporate Liabilities}. The Journal of Political Economy, 81(3): 637-654 (1973).

\bibitem{simfBM}
Dieker, T. \textit{Simulation of fractional Brownian motion}. University of Twente (2004).

\bibitem{impvol}
Fengler, M. R. \textit{Semiparametric Modelling of Implied Volatility}, 1st edition. Springer (2005).

\bibitem{volsurface}
Gatheral, J. \textit{The Volatility Surface: A Practitioner's Guide}, 1st edition. Wiley (2006).
\bibitem{volisrough}
Gatheral, J., Jaisson, T., and Rosenbaum, M. \textit{Volatility is Rough}. Quantitative Finance, 18(6):933-949 (2014).

\bibitem{heston}
Heston, S. L. \textit{A Closed-Form Solution for Options with Stochastic Volatility with Applications to Bond and Currency Options}. The Review of Financial Studies, 6(2):327-343 (1993).

\bibitem{blackscholes}
Kogan, L. \textit{Stochastic Calculus and Option Pricing}. Massachusetts Institute of Technology (2010).

\bibitem{mandelbrot}
Mandelbrot, B.B., and Van Ness, J.W. \textit{Fractional Brownian Motions, Fractional Noises and Applications}. SIAM Review, 10(4):422-437 (1968).

\bibitem{heston2}
Mikhailov, S., and Nögel, U. \textit{Heston's Stochastic Volatility Model Implementation, Calibration and some Extensions}. WILMOTT Magazine (2003).

\bibitem{fBMbook}
Nourdin, I. \textit{Selected Asepcts of Fractional Brownian Motion}, 1st edition. Springer (2012).

\bibitem{forecast}
Nuzman, C.J., and Poor, V.H. \textit{Linear Estimation of Self-Similar Processes via Lamperti's Transformation}. Journal of Applied Probability, 37(2):429-452 (2000).

\bibitem{Orimarsnoter}
Sauri, O. \textit{Stochastic Analysis and its Applications to Mathematical Finance}, Department of Mathematical Sciences, Aalborg University (2022).

\bibitem{estimationfOU}
Weilin, X., Wang, J.Y. \textit{Estimation and Inference in Fractional Ornstein-Uhlenbeck Model with Discrete-Sampled Data}. Applied Mathematical Modelling, 35(9): 4196-4207 (2011).
\end{thebibliography}{}
\addcontentsline{toc}{chapter}{\phantom{13} Bibliography}


\end{document}
